### 2022-09-02 paper/icse23/abstract.tex
icse23 submission latex

\begin{abstract}
  \Nlp (NLP) technique has become one of the core techniques for
  developing text  analytic applications.  These applications need to achieve high
  reliability to be useful in practice.  The trustworthiness of the NLP applications is often obtained by measuring the accuracy of
  the applications on holdout datasets. However, evaluating NLP on the accuracy of the holdout datasets is limited in validating its overall
  quality because these datasets are often not
  comprehensive. To address this limitation, evaluating an NLP model on
  task-specific behaviors defined on linguistic
  capabilities has been introduced. However, such evaluation relies on manually
  created test cases, and  is still limited to measure the model
  performance on limited datasets. In this work, we introduce \tool,
  an NLP model testing infrastructure.  Given a linguistic capability that users want to evaluate for a NLP model, \tool finds suitable seed inputs
  from existing datasets, generates sufficient number
  of new test inputs by expanding the seed inputs based on their \cfg
  (CFG).  We evaluate \tool by showing that it can generate test cases that are more diverse than an existing approach.
  We also show that \tool facilitates
  identification of critical failures and its origins in the NLP models
  for the \sa task.
\end{abstract}

>>>>

\begin{abstract}
  \Nlp has been widely used for developing a variety of text analytic applications with high reliability. For any NLP-based applications to be trustworthy, assessment through measuring the accuracy of the holdout datasets is needed. Recent research introduced methods that assess an NLP model on a set of linguistic capabilities.
  However, we observe that state-of-the-art methods rely on manually created test cases, which may be limited in terms of scalability and diversity.
%\Nlp (NLP) technique has become one of the core techniques fordeveloping text  analytic applications.  These applications need to achieve high reliability to be useful in practice.  
%The trustworthiness of the NLP applications is often obtained by measuring the accuracy ofthe applications on holdout datasets. However, assessing an NLP application on the accuracy of the holdout datasets is limited in validating its overallquality because these datasets are often notcomprehensive. 
  %To address this limitation, methodologies to assess an NLP model on a set oflinguistic capabilities has recently been introduced. However, current state-of-the-art methodologies rely on manuallycreated test cases which limits the scale of the testing dataset. 
  In this work, we introduce \tool,
  an automated linguistic capability-based testing technique.  Given a set of linguistic capabilities that assess an NLP model, \tool first searches for suitable seed inputs from existing datasets, and then generates a sufficient number
  of new test inputs by expanding the seed inputs based on their \cfg (CFG). 
  \tool guarantees the correctness of the generated test input labels and that these test inputs belong to the correct linguistic capabilities. 
  Evaluation results show that \tool can generate test cases that are 100\%  more diverse than state-of-the-art 
   while ensuring the correctness of labels and linguistic capabilities of the test inputs. 
%   \Cong{You mention comprehensive and scalability before, so better give improvement numbers in terms of these metrics.}
  We also show that \tool facilitates the identification of critical failures and its origins in the NLP models.
\end{abstract}

### 2022-09-02 paper/icse23/approach.tex
icse23 submission latex

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{figs/overview.pdf}
  \vspace{-6mm}
  \caption{\OverviewFigCaption}
\end{figure*}

@@

  We design and implement a new NLP model testing method,
\emph{Specification- and Syntax-based Linguistic Capability Testing
  (\tool{})}, that automatically generates test cases with oracles to assess the quality of sentiment analysis models. \tool{} addresses all three challenges discussed in Section~\ref{sec:intro}.

@@

% We present \tool{}, a new \lc test case generation
% tool, that satisfies all of these criteria.  \sw{I could not summarize
%   a cohesive idea that drives our design. Leaving it here to fill in.
%   Also, I felt my writing below still lacks justification for some
%   design choices (e.g., why we do the differentiation).}
Figure~\ref{fig:overview} shows the overview of \tool{}, which
consists of two phases.  The \emph{specification-based seed
  generation} phase performs rule-based searches from a real-world
dataset and template-based transformation to obtain the
initial seed \sents.  The search rules (e.g., search for \neu
\sents that do not include any \pstv or \ngtv words) and
transformation templates (e.g., negating a sentence) are defined in the \emph{\lc
  specifications} (Table~\ref{tab:specification}), which result in seed sentences that are most likely to conform
to a specific \lc ({\bf C2}) and is labelled
correctly ({\bf C3}).

The \emph{syntax-based \sent expansion} phase expands the seed
\sents with additional syntactic elements (i.e., words) to cover many real-world
syntactic structures ({\bf C1}). It first performs a syntax analysis
to identify the \pos (PoS) tags that can be inserted to each
seed, by comparing the PoS parse trees between the seed \sent and
many other \sents from a large reference dataset. Each identified
tag is inserted into the seed as a \emph{mask}. It then uses an NLP
recommendation model (i.e., BERT \cite{devlin2019bert}) to suggest possible
words. If a resulting \sent is validated to be consistent with the
specification which additionally defines the rules for expansion
(e.g., the expanded word should be \neu), {\bf C2} and {\bf C3} are
still satisfied.
% Last, because some validated \sents may include
% unacceptable suggested words given the context, we use a heuristic (i.e., the
% confidence score from the NLP recommendation model) to select the more
% realistic context-aware expanded \sents into \tool{}'s test suite.

@@

\subsection{Specification-based Seed Generation}
The seed generation phase of \tool starts by searching \sents in a
real-world dataset that match the rules defined in the \lc
specification, and then transforming the matched \sents using
templates to generate seed \sents that conform to individual
\lcs. The reasons for this design choice are twofold.  First, while
generally judging which \lc any \sent falls into and which label it
should have is infeasible, there exist simple rules and templates to
allow classifying the resulting \sents into individual \lcs and
with the correct labels, with high confidence.  This enables us to
test each \lc individually.  Second, searching from a real-world
dataset ensures that the \sents used as test cases for testing \lcs
are realistic and diverse. The diverse test cases are more likely to
achieve a high coverage of the target model's functionality in each
\lc, thus detecting more errors.
%
In this phase, \tool first searches and selects \sents applicable to
the \lc in a given real-world dataset with search rules. In case that
the search rules only fulfill portion of the \lc specifications, the
selected \sents are not yet ready to be used as seeds, we
transform the selected \sents into seed \sents using the
heuristic templates.
%
Table~\ref{tab:specification} shows the search rules and the
transformation templates of all 11 linguistic capabilities we
implemented in \tool. The first column shows the \lc type and its
description, and the second column shows the search rule and
transformation template used in each \lc. For LC1 and LC2, the NLP
models are evaluated in the scope of short \sents with selective
sentiment words. It does not require any
transformation because the search rules alone are sufficient to find sentences that conform
to the \lcs. On the other hand, search rules of LC3 to LC11 are not enough to match their \lc specification; thus, \tool additionally uses 
templates to transform the searched \sents to match the corresponding \lc. For example, in LC3's transformation template, the searched \sents are appended as part of a sentence to generate a seed.
In LC4's transformation template, the searched demonstrative sentences are negated.
% \sw{@Jaeseong: revise the rest of 3.1 based on
%   Table~\ref{tab:specification}. I commented out the old text but it
%   is still in the tex file.} \jl{I revised and added the explanation}

@@

For each production of in each seed's parse tree (lines 3 and 4), we
extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
the grammar symbols at the right-hand-side (line 6), $s\_rhs$. In line
7, the algorithm iterates through all productions in the reference
context-free grammar and matches these that have the same non-terminal
at the left-hand-side as $s\_lhs$.  The right-hand-side of each
matched production is called $r\_rhs$.  If $s\_rhs$ consists of a
subset of the grammar symbols in $r\_rhs$ (line 8), the additional
symbols in the $r\_rhs$ are inserted as masks in the parse tree of
the seed \sent, in their respective positions in the expanded production.
The left to right traversal of the leaves of an expanded parse tree
forms a masked \sent.  Due to a potential large number of masked \sents created by this algorithm, we randomly select $k$
masked \sents for the next \sent expansion and validation phase (line 14).
% The
% random sampling is unbiased approach since it gives same chance to be
% chosen. Thus, the random sample becomes representative of the
% population of the masked \sents, and it efficiently shows the
% usefulness of the \tool.

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.7]{figs/running_example.pdf}
  \vspace{-5mm}
  \caption{\RunningExCaption}
%  Expansion of the seed \sent ``Or
%both.''. For a \prodr in seed ``NP->[DT]'' on the left, the \prodr of
%``NP->[DT, NNS]'' is found in reference. Thus, the component NNS can be expanded in the
%seed and ``NP->[DT]'' is replaced with ``NP->[DT, NNS]'' and it generates new
%expanded \sent on the right.
\end{figure*}

\paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
to generate a masked \sent. The \sent ``Or both." is a seed of the \lc of
\SareqExOne.  The tree on the left shows the parse tree of this seed;
it consists of two productions: ``FRAG->[CC, NP, .]" and ``NP->[DT]".
When matching the left-hand-side non-terminal of the second production
(i.e., ``NP") in the reference CFG, we found that it includes a
production ``NP->[DT, NNS]" which has an additional symbol ``NNS" on
the right-hand-side.  The algorithm thus expands the parse tree with
this symbol, shown in the second tree.  The masked \sent ``Or both
\{MASK\}." is the result of the left-to-right traversal of this
expanded parse tree.

@@

In this phase, the words to fill in the masks in the masked \sents are
suggested by the BERT model~\cite{devlin2019bert}. 
BERT is a transformer-based \nl model that is pre-trained on two tasks: masked token prediction and next sentence prediction. BERT model is capable of suggesting words for the masked
token according to its surrounding context in a \sent. For each masked
token, multiple words are suggested, ranked by their confidence scores.
% \sw{Algorithm 1 does not require we only have one mask in the masked
%   \sent. Can the model suggest multiple words at the same time?}
% \jl{yes. it can predict multiple masked tokens at the same time.}
% \jl{I added the explanation of BERT}
%
Because BERT model is not aware of the \lc
specification and the grammar symbol in the expanded parse tree, an
expanded \sent using the suggested words may no longer satisfy the
\lc specification. Therefore, we perform validation
on the suggested words and only accept them if the following three
criteria are met.

First, the PoS tag of the suggested word must match the PoS tag of the
expanded symbol in the parse tree. For the example in
Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
noun); thus, the suggested word must also be a ``NNS". We use \spacy \cite{spacy}, a free open-source library for \nlp, to extract the PoS
tag for each suggested word.

Second, it is required that the
sentiment of the expanded \sent is the same as the seed \sent. To
ensure this, the suggested words must be \neu.

Third, we additionally verify that the
expanded \sents satisfy the same search rules for the seed
\sent in LC1 and LC2. This criteria cannot be applied to other linguistic capabilities because they have additional transformation templates.

@@

\paragraph{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
by BERT. For this masked \sent, BERT suggested six words. Each word
is associated with the confidence score provided by BERT, the PoS tag,
and the sentiment. Among the six words, only ``ways'' and ``things''
are validated by \tool{} because they have the Pos tag ``NNS'' and are
\neu. In addition, it is found that both \sents meets the search
rule of the associated \lc of \SareqExOne. In the end, two \sents
of ``Or both ways'' and ``Or both things'' are generated.

>>>>

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.85\linewidth]{figs/overview.pdf}
  \vspace{-2mm}
  \caption{\OverviewFigCaption}
\end{figure*}

@@

  We design and implement a new NLP model testing method,
\emph{Specification- and Syntax-based Linguistic Capability Testing
  (\tool{})}, which automatically generates test cases with oracles to assess the quality of NLP models.
%   \tool{} addresses the challenges discussed in Section~\ref{sec:intro}. \sw{Revisit overview part of this section when intro is revised (see if these three challenges are still listed).}

@@

% We present \tool{}, a new \lc test case generation
% tool, that satisfies all of these criteria.  \sw{I could not summarize
%   a cohesive idea that drives our design. Leaving it here to fill in.
%   Also, I felt my writing below still lacks justification for some
%   design choices (e.g., why we do the differentiation).}
Figure~\ref{fig:overview} depicts an overview of \tool{}, which
consists of two phases.  The \emph{specification-based seed
  generation} phase performs rule-based searches from a real-world
dataset and template-based transformation to obtain the
initial seed \sents.  The search rules (e.g., search for \neu
\sents that do not include any \pstv or \ngtv words) and
transformation templates (e.g., negating a sentence) are defined in the \emph{\lc
  specifications} (Table~\ref{tab:specification}). Using the specification will result in seed sentences that are most likely to conform
to a specific \lc and is labelled
correctly.

The \emph{syntax-based \sent expansion} phase expands the seed
\sents with additional syntactic elements (i.e., words) to cover many more real-world
syntactic structures. It first performs a syntax analysis
to identify the \pos (PoS) tags that can be inserted to each
seed, by comparing the PoS parse trees between the seed \sent and
many other \sents from a large reference dataset. Each identified
tag is inserted into the seed as a \emph{mask}. It then uses an NLP
recommendation model (i.e., BERT \cite{devlin2019bert}) to suggest possible
words.
Finally, the resulting \sent is validated to be consistent with the
specification which additionally defines the rules for expansion
(e.g., the expanded word should be \neu).
% Last, because some validated \sents may include
% unacceptable suggested words given the context, we use a heuristic (i.e., the
% confidence score from the NLP recommendation model) to select the more
% realistic context-aware expanded \sents into \tool{}'s test suite.

@@

\subsection{Specification-based Seed Generation}
The seed generation phase of \tool starts by searching \sents in a real-world dataset, which match the rules defined in the \lc
specification, and then transforming the matched \sents using
templates to generate seed \sents that conform to individual
\lcs. The reasons for this design choice are twofold.  First, while it is generally infeasible to judge which \lc any \sent falls into and which label it
should have, there exist simple rules and templates that 
allow for classifying the resulting \sents into individual \lcs and
with the correct labels, with high confidence.  This enables us to
test each \lc individually.  Second, searching from a real-world
dataset ensures that the \sents used as test cases for testing \lcs
are realistic and diverse. The diverse test cases are more likely to
achieve a high coverage of the target model's functionality in each
\lc, thus detecting more errors.

Specifically, \tool first searches and selects \sents applicable to
the \lc in a given real-world dataset with search rules. In case
the search rules only fulfill part of the \lc specifications (i.e., LC3-LC10 in Table \ref{tab:specification}), we then
transform the selected \sents into seed \sents using the
heuristic templates.

Table~\ref{tab:specification} shows the search rules and the
transformation templates of all 10 linguistic capabilities we
implemented in \tool. The first column shows the \lc type and its
description, and the second column shows the search rule and
transformation template used in each \lc. For LC1 and LC2, the NLP
models are evaluated in the scope of short \sents with selective
sentiment words. It does not require any
transformation because the search rules alone are sufficient to find sentences that conform
to the \lcs. On the other hand, search rules of LC3 to LC10 are not enough to match their \lc specification; thus, \tool additionally uses 
templates to transform the searched \sents to match the corresponding \lc. For example, in LC3's transformation template, the searched \sents are appended as part of a sentence to generate a seed.
In LC4's transformation template, the searched demonstrative sentences are negated.
% \sw{@Jaeseong: revise the rest of 3.1 based on
%   Table~\ref{tab:specification}. I commented out the old text but it
%   is still in the tex file.} \jl{I revised and added the explanation}

@@

For each production in each seed's parse tree (lines 3 and 4), we
extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
the grammar symbols at the right-hand-side (line 6), $s\_rhs$. In line
7, the algorithm iterates through all productions in the reference
context-free grammar and matches these that have the same non-terminal
at the left-hand-side as $s\_lhs$.  The right-hand-side of each
matched production is called $r\_rhs$.  If $s\_rhs$ consists of a
subset of the grammar symbols in $r\_rhs$ (line 8), the additional
symbols in the $r\_rhs$ are inserted as masks in the parse tree of
the seed \sent, in their respective positions in the expanded production.
The left to right traversal of the leaves of an expanded parse tree
forms a masked \sent.  Due to a potential large number of masked \sents created by this algorithm, we randomly select $k$
masked \sents for the next \sent expansion and validation phase (line 14).
% The
% random sampling is unbiased approach since it gives same chance to be
% chosen. Thus, the random sample becomes representative of the
% population of the masked \sents, and it efficiently shows the
% usefulness of the \tool.

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.6]{figs/running_example.pdf}
  \vspace{-5mm}
  \caption{\RunningExCaption}
%  Expansion of the seed \sent ``Or
%both.''. For a \prodr in seed ``NP->[DT]'' on the left, the \prodr of
%``NP->[DT, NNS]'' is found in reference. Thus, the component NNS can be expanded in the
%seed and ``NP->[DT]'' is replaced with ``NP->[DT, NNS]'' and it generates new
%expanded \sent on the right.
\end{figure*}

\paragraph*{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
to generate a masked \sent. The \sent ``Or both." is a seed of the \lc of
\SareqExOne.  The tree on the left shows the parse tree of this seed;
it consists of two productions: $``FRAG\rightarrow[CC, NP, .]"$ and $``NP\rightarrow[DT]"$.
When matching the left-hand-side non-terminal of the second production
(i.e., $``NP"$) in the reference CFG, we found that it includes a
production $``NP\rightarrow[DT, NNS]"$ which has an additional symbol ``NNS" on
the right-hand-side.  The algorithm thus expands the parse tree with
this symbol, shown in the second tree.  The masked \sent ``Or both
\{MASK\}." is the result of the left-to-right traversal of this
expanded parse tree.

@@

In this phase, the words to fill in the masks in the masked \sents are
suggested by the BERT model~\cite{devlin2019bert}. 
BERT is a transformer-based \nl model that is pre-trained on two tasks: masked token prediction and next sentence prediction. BERT model is capable of suggesting words for the masked
token according to its surrounding context in a \sent. For each masked
token, multiple words may be suggested, ranked by their confidence scores.
% \sw{Algorithm 1 does not require we only have one mask in the masked
%   \sent. Can the model suggest multiple words at the same time?}
% \jl{yes. it can predict multiple masked tokens at the same time.}
% \jl{I added the explanation of BERT}
%
Because BERT model is not aware of the \lc
specification and the grammar symbol in the expanded parse tree, an
expanded \sent using the suggested words may no longer satisfy the
\lc specification. Therefore, we perform validation
on the suggested words and only accept them if the following three
criteria are met.

First, the PoS tag of the suggested word must match the PoS tag of the
expanded symbol in the parse tree. For the example in
Figure~\ref{fig:ExpEx}, the masked symbol is a $``NNS"$ (i.e., plural
noun); thus, the suggested word must also be a $``NNS"$. We use \spacy \cite{spacy}, a free open-source library for \nlp, to extract the PoS
tag for each suggested word.
Second, the
sentiment of the expanded \sent must be the same as the seed \sent. To
ensure this, we require the suggested words be \neu. 
Third, we additionally verify that the
expanded \sents satisfy the same search rules for the seed
\sents in LC1 and LC2. This criteria cannot be applied to other linguistic capabilities because they have additional transformation templates.

@@

\paragraph*{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
by BERT. For this masked \sent, BERT suggested six words. Each word
is associated with the confidence score provided by BERT, the PoS tag,
and the sentiment. Among the six words, only ``ways'' and ``things''
are validated by \tool{} because they have the Pos tag ``NNS'' and are
\neu. In addition, both \sents still meet the search
rule of the associated \lc of \SareqExOne. In the end,  the syntax-based sentence expansion results in two \sents, ``Or both ways.'' and ``Or both things.'', from the seed ``Or both.".

### 2022-09-02 paper/icse23/background.tex
icse23 submission latex

%% \sw{We should motivate the testing of linguistic capabilities. Give
%%   background of the work that has been done in CheckList: what
%%   capabilities they support and their limitations. Maybe find a
%%   motivating example?}

In this section, we provide a brief background of \Cklst's approach of test case generation
 via an example.
%  Quality of software is verified by ensuring
% the proper working of all functionalities without knowing the internal
% workings of the software. Knowing performances of model on the
% multiple functionalities provides users with better understanding and
% debugging the software. The same principle applies to the NLP model.
% Traditional NLP model evaluation relying on a test set lacks the
% specification of model functionality. However, in NLP domain, there
% are many phenomena on linguistic input such as negation, and
% questionization. Given a NLP task, the phenomena determine
% task-relevant output. Traditional evaluation method neglects them;
% thus, it becomes less efficient to detect and analyze which aspect the
% model yields unexpected outcome.
\Cklst
introduces task-dependent \lcs for monitoring model performance on
each \lc. It assumes that the linguistic phenomena can be represented
in the behavior of the model under test, because each linguistic capability specifies the desired behavior between inputs and outputs. For each \lc, \Cklst creates
test case templates and generates sentences by filling in the values of
each placeholder.

We show an example of \Cklst templates in
Figure~\ref{code:TempEx}. These templates are used for
evaluating a \sa model on the linguistic capability of \SareqExThree.
For the templates defined
from lines~\ref{code:tempex:template:1} to \ref{code:tempex:template:2}, they
have placeholders such as ${it}$, ${air\_noun}$, ${pos\_adj}$. Values
for the placeholders are defined at
line~\ref{code:tempex:airnoun:1},~\ref{code:tempex:posadj:1} and~\ref{code:tempex:itbe}, .
For each template, \Cklst fills in all the combinations of the
values of placeholders, and
the sentences such as ``The flight is good'', ``That
airline was happy'' are generated. These sentences are used for the evaluation
of the \lc.

Despite its simplicity of test case generation, \Cklst has
limitations. First, it relies on manual work for defining template
structure and its placeholder values making the test case
generation a costly process. Moreover, such
manual work generates the limited number of templates and produces high similarity between test cases, and induces bias in the test cases. These limitations motivated the design of our approach.

\begin{figure}[hbp!]
 \centering
 \lstinputlisting[language=python-pretty]{code/checklist_template.py}
 \vspace{-10pt}
 \caption{\CklstTemplateFigCaption}
 \vspace{-10pt}
\end{figure}

>>>>

In this section, we provide a brief background of \Cklst's \cite{marcoACL2020checklist} approach of test case generation
 via an example.
%  Quality of software is verified by ensuring
% the proper working of all functionalities without knowing the internal
% workings of the software. Knowing performances of model on the
% multiple functionalities provides users with better understanding and
% debugging the software. The same principle applies to the NLP model.
% Traditional NLP model evaluation relying on a test set lacks the
% specification of model functionality. However, in NLP domain, there
% are many phenomena on linguistic input such as negation, and
% questionization. Given a NLP task, the phenomena determine
% task-relevant output. Traditional evaluation method neglects them;
% thus, it becomes less efficient to detect and analyze which aspect the
% model yields unexpected outcome.
\Cklst
introduces task-dependent \lcs for monitoring model performance on
each \lc. It assumes that the linguistic phenomena can be represented
in the behavior of the model under test, because each linguistic capability specifies the desired behavior between model inputs and outputs. For each \lc, \Cklst manually creates
test case templates and generates sentences by filling in the values of
each placeholder.

\begin{figure}[t]
 \centering
 \lstinputlisting[language=python-pretty]{code/checklist_template2.py}
 \vspace{-10pt}
 \caption{\CklstTemplateFigCaption}
 \vspace{-10pt}
\end{figure}

We show an example of \Cklst templates in
Figure~\ref{code:TempEx}. These templates are used for
evaluating the \sa model on the linguistic capability of \SareqExThree.
For the templates defined
at lines~\ref{code:tempex:template:1} to \ref{code:tempex:template:2}, they
have placeholders such as ${it}$, ${air\_noun}$, ${pos\_adj}$. Values
for the placeholders are defined at
lines~\ref{code:tempex:airnoun:1} to~\ref{code:tempex:negadj:2}.
For each template, \Cklst fills in all the combinations of the
values of placeholders to generate sentences under this \lc.
For example, sentences such as ``The flight is good'' and ``That
airline was happy'' are generated using the template at line 10.

Despite the simple approach used for test case generation, \Cklst has
limitations. First, it relies on manual work for defining template
structure and its placeholder values, making the test case
generation a costly process. Moreover, such
manual work generates a limited number of templates, produces similar test cases, and induces bias in the test cases. These limitations motivated the design of our approach.

### 2022-09-02 paper/icse23/related.tex
icse23 submission latex

\MyPara{NLP Testing}
%
With the increasing use of NLP models, evaluation of NLP models is
becoming a more important issue. Apart from the accuracy-based testing
scheme, recent works have considered model robustness as an
aspect for evaluation. Belinkov and Bisk
\textit{\etal}~\cite{belinkov2018breaknmt} aimed to fail neural machine
translation model by intentionally introducing noise in the input
text. Pinjia
\textit{\etal}~\cite{pinjia2020structinvtestingnmt,pinjia2020testnmtrt}
measured the robustness by assuming syntactic and semantic relation
between input and output of neural machine translation model.  Ribeiro
\textit{\etal}~\cite{ribeiro2018sear} proposed an approach to
generalize semantically equivalent adversarial rules. In addition,
Rychalska \textit{\etal}~\cite{rychalska2019wildnlp} measured drops in
BLEU scores by corruption operation, and compared model robustness
based on the amount of the drops. Iyyer
\textit{\etal}~\cite{iyyer2018adversarial} introduced learning-based
model for adversarial data augmentation.

In addition to the
robustness on adversarial set, various other aspects of the NLP model have been
considered for the robustness evaluation. Prabhakaran
\textit{\etal}~\cite{prabhakaran2019fairness} developed an evaluation
framework to detect unintended societal bias in NLP models. Rottger
\textit{\etal}~\cite{rottger2020hatecheck} introduced a functional
test suite for hate speech detection in the NLP model.  Ribeiro
\textit{\etal}~\cite{ribeiro2019consistencyeval} measured logical
consistency of NLP model. These techniques evaluate the robustness of
the NLP model. However, we focused on the evaluation of model capability
over multiple perspectives and produce debugging information by comparing
seed and expanded test cases.

\MyPara{Linguistic Capability Evaluation}
%
Wang \textit{\etal}~\cite{wang2018glue, wang2019superglue} proposed
multiple diagnostic datasets to evaluate NLP models. These datasets
evaluate NLP model's ability to understand input sentence via natural
language inference problems. More recently, \Cklst proposed an evaluation
method of input-output behavior defined as \lcs. \Cklst generates
behavior-guided inputs for validating the
behaviors.~\cite{marcoACL2020checklist}. Unlike prior work that relies on manual
test case generation, we used structural information in text to
generate test cases automatically.

@@

>>>>

\MyPara{NLP Testing}
%
% With the increasing use of NLP models, evaluation of NLP models is
% becoming a more important issue. 
Apart from the accuracy-based testing
scheme, recent works have considered model robustness as an
aspect for evaluation. Belinkov and Bisk
\textit{\etal}~\cite{belinkov2018breaknmt} aimed to fail Neural Machine
Translation (NMT) model by intentionally introducing noise in the input
text. Pinjia
\textit{\etal}~\cite{pinjia2020structinvtestingnmt,pinjia2020testnmtrt}
measured the robustness of NMT model by assuming syntactic and semantic relation between input and output. Ribeiro
\textit{\etal}~\cite{ribeiro2018sear} proposed an approach to
generalize semantically equivalent adversarial rules. Rychalska \textit{\etal}~\cite{rychalska2019wildnlp} measured drops in
BLEU by corruption operation, and compared model robustness
based on the amount of the drops. Iyyer
\textit{\etal}~\cite{iyyer2018adversarial} introduced learning-based
model for adversarial data augmentation.

In addition to the
robustness on adversarial set, various other aspects of the NLP model have been
considered for the robustness evaluation. Prabhakaran
\textit{\etal}~\cite{prabhakaran2019fairness} developed an evaluation
framework to detect unintended societal bias in NLP models. Rottger
\textit{\etal}~\cite{rottger2020hatecheck} introduced a functional
test suite for hate speech detection in the NLP model.  Ribeiro
\textit{\etal}~\cite{ribeiro2019consistencyeval} measured logical
consistency of NLP model. However, in this work, we focused on the model evaluation over multiple perspectives and produced debugging information by comparing seed and expanded test cases.

\MyPara{Text Generation}
%
Different data augmentation approaches have been proposed for text generation. One of methods in this category is easy data augmentation (EDA)~\cite{weizou2019eda}. It uses simple operations such as synonym replacement and random swap. Coulombe~\cite{coulombe2018textaugapi} implements rule-based transformations using regular expressions for text transformations such as insertion of spelling mistakes, data alterations, entity names, and abbreviations. Mixup interpolation, which was introduced in computer vision category, was implemented in text domain~\cite{hongyu2019dataaugmixup}. Learning-based language models has been used to generate text data for multiple tasks~\cite{qizhe2019unsupdataaug, ateret2019lambda}. While these approaches focus on obtaining synthetic training data, not testing NLP model over \lcs,
% they are not able to be used for the capability testing of the NLP model, 
our work generates text data for testing NLP model over \lcs.

\MyPara{Linguistic Capability Evaluation}
%
Wang \textit{\etal}~\cite{wang2018glue, wang2019superglue} proposed
multiple diagnostic datasets to evaluate NLP models 
% . These datasets
% evaluate NLP model's ability to understand input sentence
via natural language inference problems. More recently, \Cklst proposed an evaluation
method of input-output behavior defined as \lcs. \Cklst generates
behavior-guided inputs for validating the
behaviors.~\cite{marcoACL2020checklist}. Unlike prior work that relies on manual
test case generation, we used structural information in text to
generate test cases automatically.

@@

% [1] Li Z, Ma X, Xu C, et al. Structural coverage criteria for neural networks could be misleading[C]//2019 IEEE/ACM 41st International Conference on Software Engineering: New Ideas and Emerging Results (ICSE-NIER). IEEE, 2019: 89-92.

% [2] Harel-Canada F, Wang L, Gulzar M A, et al. Is neuron coverage a meaningful measure for testing deep neural networks?[C]//Proceedings of the 28th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering. 2020: 851-862.

% [3] Yan S, Tao G, Liu X, et al. Correlations between deep neural network model coverage criteria and model quality[C]//Proceedings of the 28th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering. 2020: 775-787.

% [4] Chen J, Yan M, Wang Z, et al. Deep neural network test coverage: How far are we?[J]. arXiv preprint arXiv:2010.04946, 2020.
% [5] Xie Q, Dai Z, Hovy E, et al. Unsupervised data augmentation for consistency training[J]. Advances in Neural Information Processing Systems, 2020, 33: 6256-6268.

% [6] Coulombe C. Text data augmentation made simple by leveraging nlp cloud apis[J]. arXiv preprint arXiv:1812.04718, 2018.

% [7] Wei J, Zou K. Eda: Easy data augmentation techniques for boosting performance on text classification tasks[J]. arXiv preprint arXiv:1901.11196, 2019.

% [8] Guo H, Mao Y, Zhang R. Augmenting data with mixup for sentence classification: An empirical study[J]. arXiv preprint arXiv:1905.08941, 2019.

% [9] Anaby-Tavor A, Carmeli B, Goldbraich E, et al. Do not have enough data? Deep learning to the rescue![C]//Proceedings of the AAAI Conference on Artificial Intelligence. 2020, 34(05): 7383-7390.
